Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-19 ICLR25/introduction.tex
update reference

Deep neural networks (DNNs for short) have demonstrated remarkable capabilities, achieving human-like or even superior performance across a wide range of tasks. However, their robustness is often compromised by their susceptibility to input perturbations \cite{szegedy}. This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{katz2019marabou,Reluplex,deeppoly}. This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools. While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way. 
For the past 5 years, VNNcomp has focused on rather easy instances, that can be solved within tens of seconds (the typical hard time-out is 300s). For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances. Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp24}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
We will thus focus in the following mostly on $\alpha,\beta$-CROWN.

@@

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 30\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  5588s & 6100s
		  \\  \hline
	\end{tabular}
\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
\label{table_complete}
\end{table}

>>>>

Deep neural networks (DNNs for short) have demonstrated remarkable capabilities, achieving human-like or even superior performance across a wide range of tasks. However, their robustness is often compromised by their susceptibility to input perturbations \cite{szegedy}. This vulnerability has catalyzed the verification community to develop various methodologies, each presenting a unique balance between completeness and computational efficiency \cite{katz2019marabou,Reluplex,deeppoly}. This surge in innovation has also led to the inception of competitions such as VNNComp \cite{VNNcomp}, which aim to systematically evaluate the performance of neural network verification tools. While the verification engines are generic, the benchmarks usually focus on local robustness, i.e. given a DNN, an image and a small neighbourhood around this image, is it the case that all the images in the neighbourhood are classified in the same way. 
For the past 5 years, VNNcomp has focused on rather easy instances, that can be solved within tens of seconds (the typical hard time-out is 300s). For this reason, DNN verifiers in the past years have mainly focused on optimizing for such easy instances. Among them, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, and PyRAT, respectively 4th, 3rd and 2sd of the last VNNcomp'24 \cite{VNNcomp24}
and 5th, 2sd and 3rd  of the VNNcomp'23 \cite{VNNcomp23}; MnBAB \cite{ferrari2022complete}, 2sd in VNNcomp'22 \cite{VNNcomp22}, built upon ERAN \cite{deeppoly} and PRIMA \cite{prima}; and importantly, $\alpha,\beta$-CROWN \cite{crown,xu2020fast}, the winner of the last 4 VNNcomp, benefiting from branch-and-bound based methodology \cite{cutting,BaB}.
We will thus focus in the following mostly on $\alpha,\beta$-CROWN.

@@

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum? &  Full MILP  \\ \hline
		MNIST 6$\times$100 & 99\% & 90\% & 28\% & $\approx 46\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  5220s & 6100s
		  \\  \hline
	\end{tabular}
\caption{Complete verifiers run on the smallest of the hard DNN with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
No complete verifier could outperform $\alpha,\beta$-CROWN (40\%, 1026s), despite the much larger runtime.}
\label{table_complete}
\end{table}
